### 2014-07-23 MS.tex
legend figs 1,2,3

\texttt{Figure 1.} Results of the MEDUSA analysis run on the maximum
clade credibility tree from Reference 10. Estimated rate shifts in Table 1.

\texttt{Figure 2.} Boxplot of the range of diversification values for
tips or clades estimated by MEDUSA on the 1000 random trees from the
posterior distribution of the Nymphalidae phylogeny. The tips or clades
shown are those present on the maximum clade credibility tree from
Reference 10.

\texttt{Figure 3.} Results of the MultiMEDUSA analysis on 1000 randomly
sampled trees from the posterior distribution of the Nymphalidae
phylogeny. Bars show the probability for nodes of being recovered as
significant increases or decreases in net diversification rates by
MultiMEDUSA.

>>>>

\texttt{Figure 1.} MEDUSA analysis run on the MCT 
from Reference 10. Estimated rate shifts in Table 1.

\texttt{Figure 2.} Range of diversification values for
tips or clades estimated by MEDUSA on the 1000 random trees.

\texttt{Figure 3.} Results of the MultiMEDUSA analysis showing
the probability for nodes of being recovered as diversification events.
